Structuring College Access

### 2025-02-26 index.qmd
changing metro orders and all figures

knitr::opts_chunk$set(echo = F, message = F)

@@

  # Convert spaces -> underscores for filenames
  metro_underscored <- str_replace_all(metro, " ", "_")

  # Build the three file paths (PNG, title TXT, note TXT)
  fig_file  <- file.path(base_path, rq, str_c(rq, "_", metro_underscored, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, str_c(rq, "_", metro_underscored, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, str_c(rq, "_", metro_underscored, "_", graph_type, "_note.txt"))

@@

# 2) Define your metros / RQs
metros <- c(
  "atlanta",
  "bay area",
  "boston",
  "chicago",
  "cleveland",
  "dallas",
  "dc maryland virginia",
  "detroit",
  "houston",
  "long island",
  "los angeles",
  "miami",
  "new york city",
  "northern new jersey",
  "orange county",
  "philadelphia",
  "san diego"
)

@@

# 3) Subset of metros with RQ2 data (2 orders each)
rq2_metros <- c(
  "chicago", "philadelphia", "los angeles", 
  "orange county", "san diego", "bay area",
  "northern new jersey","long island",'detroit','dallas','houston'
)

# We'll define a "metro_orders" list for those RQ2 metros:
metro_orders <- list(
  "chicago"             = c("487984", "488035_488053"),
  "philadelphia"        = c("448922", "448427_448440"),
  "northern_new_jersey" = c("448922", "448427_448440"),
  "long_island"         = c("448922", "448427_448440"),
  "detroit"             = c("448922", "448427_448440"),
  "dallas"              = c("448922", "448427_448440"),
  "los_angeles"         = c("448375", "448374_448420"),
  "orange_county"       = c("448375", "448374_448420"),
  "san_diego"           = c("448375", "448374_448420"),
  "bay_area"            = c("448375", "448374_448420"),
  'houston'             = c('329702') #   # houston = c('houston', 'houston_eps_codes', 'PSAT score 1010 - 1520', '329702')

)

@@

  # Print a top-level heading for the metro area
  writeLines(str_c("## ", tools::toTitleCase(m), " area"))

@@

      # Each metro has 2 plots: "race" & "ses"
      for (i in seq(graph_types_rq1)) {
        g <- graph_types_rq1[i]

        writeLines(str_c("### Research question ", rq_num, if_else(i == 1, "", " {.hide}")))
        insert_figure(rq = rq, metro = m, graph_type = g)
      }

@@

      rq1_map <- if_else(
        m == 'los angeles',
        'https://rq1-map-los-angeles.netlify.app',
        str_c('./results/maps/rq1_map_', str_replace_all(m, " ", "_"), '.html')
      )

@@

      # Convert name -> underscores for matching list keys
      m_underscored <- str_replace_all(m, " ", "_")
      orders_for_m  <- metro_orders[[m_underscored]]

      # If a metro isn't in the list or has no orders, skip
      if (is.null(orders_for_m)) next

      # We'll do 2 group types: race & firstgen
      for (i in seq(graph_types_rq2)) {
        g <- graph_types_rq2[i]

@@

              # e.g. "rq2_chicago_race_col_plot_487984.png"
              graph_type_col <- str_c(g, "_", rc, "_plot_", order_id)
              insert_figure(rq = rq, metro = m, graph_type = graph_type_col)
            }

@@

      # -------------------------------------------
      # ADDITIONAL: race_by_firstgen for each order
      # -------------------------------------------
      # Like the column approach, one slide per order_id
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num, " {.hide}"))
        # Filenames look like:
        #   rq2_northern_new_jersey_order_448922_race_by_firstgen.png
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = rq, metro = m, graph_type = graph_type_rbf)
      }

@@

      writeLines(str_c('<iframe data-src="./results/maps/rq2_map_', str_replace_all(m, " ", "_"), '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))
      writeLines('<p class="fullscreen">Fullscreen</p>')

>>>>

knitr::opts_chunk$set(echo = FALSE, message = FALSE)

@@

  # 'metro' is already underscored (e.g. "los_angeles").
  # We'll use it directly for file paths, but if you want
  # to be extra safe, you can do:
  # metro_underscored <- str_replace_all(metro, " ", "_")
  # ... (assuming it has no spaces).

  fig_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_note.txt"))

@@

# 2) Define your *underscored* metros / RQs
metros <- c(
  "atlanta",
  "bay_area",
  "boston",
  "chicago",
  "cleveland",
  "dallas",
  "dc_maryland_virginia",
  "detroit",
  "houston",
  "long_island",
  "los_angeles",
  "miami",
  "new_york_city",
  "northern_new_jersey",
  "orange_county",
  "philadelphia",
  "san_diego"
)

@@

# 3) Read the CSV (underscored metro column)
orders_df <- read_csv("scripts/metro_orders.csv")

# Derive the RQ2 metros from the CSV
rq2_metros <- unique(orders_df$metro)

@@

  # Convert "los_angeles" -> "Los Angeles" for display in slides
  heading_text <- gsub("_", " ", m, fixed = TRUE)
  heading_text <- tools::toTitleCase(heading_text)

  # Print a top-level heading for the metro area in user-friendly form
  writeLines(str_c("## ", heading_text, " area"))

@@

      # Each metro has 2 plots: "race" & "ses"
      for (i in seq_along(graph_types_rq1)) {
        g <- graph_types_rq1[i]

        # The first RQ1 slide for a metro has a real heading;
        # subsequent ones are hidden slides (".hide")
        writeLines(str_c("### Research question ", rq_num, if_else(i == 1, "", " {.hide}")))
        insert_figure(rq = rq, metro = m, graph_type = g)
      }

@@

      # Use 'm' for the file path to the map (underscored version).
      # If you had a special case for "los_angeles", you could handle that here.
      rq1_map <- str_c('./results/maps/rq1_map_', m, '.html')

      # But let's illustrate one special example for "los_angeles":
      if (m == "los_angeles") {
        rq1_map <- 'https://rq1-map-los-angeles.netlify.app'
      }

@@

      # Filter orders_df to just rows for this underscored metro
      df_metro <- filter(orders_df, metro == m)

      # If none, skip
      if (nrow(df_metro) == 0) next

      # Gather all the underscore-delimited order_ids
      orders_for_m <- df_metro$order_ids

      # We'll do 2 group types: race & firstgen
      for (i in seq_along(graph_types_rq2)) {
        g <- graph_types_rq2[i]

@@

              # e.g. "race_col_plot_448375_546954"
              # => "rq2_los_angeles_race_col_plot_448375_546954.png"
              graph_type_col <- str_c(g, "_", rc, "_plot_", order_id)
              insert_figure(rq = rq, metro = m, graph_type = graph_type_col)
            }

@@

      # -------------------------------------------
      # ADDITIONAL: "race_by_firstgen" => goes to RQ2B
      # -------------------------------------------
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num, " {.hide}"))
        # e.g. "rq2b_los_angeles_order_448375_546954_race_by_firstgen.png"
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = "rq2b", metro = m, graph_type = graph_type_rbf)
      }

@@

      writeLines(str_c(
        '<iframe data-src="./results/maps/rq2_map_',
        m,
        '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'
      ))
      writeLines('<p class="fullscreen">Fullscreen</p>')
